Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-06 gibbs.tex
Alternative titles added
Update gibbs.tex

The estimated $W^{id}$ values are provided in the fifth column of the table, for five triplets of $\cs^f$, $\cs^p$,$\cs^b$ values .
$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies as the sum of corresponding compressions in \emph{closed} and \emph{open} systems, $W_{\mathrm{id}}$ is the estimation based on the equation \refeq{eq:SEC} and $R_w$ is the corresponding recovery ratio.
Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.

\section{Conclusions}
We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited amount of water.
We have shown that in the case of gel made of strong polyelectrolyte, the compression always decreases the surrounding salinity.
We have modeled the process of water desalination by combining two processes: 
(1) the swelling of the gel in \emph{open} system, exchanging ions with a big reservoir at constant salinity. 
(2) the compression of the gel in \emph{closed} system, when the gel affects the salinity in the surrounding solution.
We estimated the energy needed to produce one liter of water and have shown that the method may compete with the modern technologies used in modern industry.

\subsection{Study limitations}
TODO

\subsection{Implications and future perspectives}
TODO

>>>>

The estimated $W^{id}$ values are provided in the fifth column of the table, for five triplets of $\cs^f$, $\cs^p$,$\cs^b$ values .
$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies as the sum of corresponding compressions in \emph{closed} and \emph{open} systems, $W_{\mathrm{id}}$ is the estimation based on the equation \refeq{eq:SEC} and $R_w$ is the corresponding recovery ratio.
\todoi{how the integration was performed}
Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.

\subsection{Study limitations}
Like other simulation based studies, our research has a limited validity,
primarily resulting from the simplifications applied in the used model.
For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
However, these limitations are also the advantage of our model because the results of our study
can be applied to similar systems, including polybasic gels with all the charges reversed.

\subsection{Implications and future perspectives}
We are aware that the concept introduced in this simulation study need to be experimentally verified.
Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.

\section{Conclusions}
We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
We have modeled the process of water desalination by sequential combinations of two processes: 
(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
We estimated the energy consumtion of this process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
We have shown that this method may compete with the modern technologies used in modern industry. \todoi{energy costs of other desalination methods???}
